Video Ads have been priced historically based on cost per million impressions(CPM) model for impressions served as it has been nearly impossible to know how much of these video ads lead to a product sale or if they even positively improve the ad-spend ROI for the advertisers topline. Viewers do not know what action to take \& how leaving them confused to figure out how to follow up on the video ad they just saw, leading to viewer engagement drop off leading to lower sales \& \underline{poor ad performance}. Hence it has \underline{not} been easy to measure ROI, effectiveness \& performance of video ads historically.

Using interactive Hoot AR augmented reality ads with obvious call to actions i.e., buy button or rent button below the interactive Hoot AR ad, sales can be generated immediately after the viewer interacts with the Hoot AR ad. Payments or micro-payments are collected using crypto-currencies such as bitcoin, eth, litecoin \& monero. Hoot is now able to price the ads based on sales referred from the user interaction with AR ad(referrals). So instead of ROI blind pricing based on impressions(CPM) we can price \underline{ROI aware} based on \underline{cost per referral(CPR)}. The CPR price becomes the primary signal that drives the continuous Vickrey auction engine that powers the Hoot ad marketplace underlineasizing the importance of ad-spend ROI and value of referrals to the advertisers. Since \underline{CPR video ads perform 10x better than CPM ads} they do not need to be shown as frequently as CPM ads to generate the same revenue, hence showing more relevant ads with higher conversions less frequently than CPM video ads leads to a \underline{quantifiably superior user experience}. By bringing about an innovative CPR based business model to video ads using Augmented reality \underline{call-to-actions} we bring the effectiveness of Google AdWords to video ads that thus far only performs as poorly as CPM banner ads. Google Adwords \& Amazon affiliate program proved \underline{conversions} \& \underline{referrals} are more valuable than impressions in keyword advertising \& e-commerce respectively. We want to bring this accountability to the video ad world by ushering in CPR based performance pricing model. Hence Hoot AR ads with AR call to actions \& interactivity, improves the effectiveness of plain video ads, leading to a quantum improvement in video ad-spend ROI very much like AdWords improved the ROI of web based banner ads, laying the foundation for a multi-billion dollar ads business. 
