

\section{the GPUCoin Foundation and Governance} % (fold)
\label{sec:the_foundation_and_governance}
% As a company limited by guarantee established in Switzerland, t
The GPUCoin Foundation's primary objective is to promote the real world application of the GPUCoin Decentralized Open Live-Streaming platform. It also aims to initially develop the GPUCoin platform and advocate governance and transparency for the platform. The GPUCoin Foundation will establish an association consisting of members of the GPUCoin ecosystem, which will be empowered to determine the direction of functionality and improvement to the GPUCoin Distributed GPU accelerate computing, mining platform and associated ecosystem.
% section the_foundation_and_governance (end)

\subsection{The dispute resolution process} % (fold)
\label{sub:the_dispute_resolution_process}
The GPUCoin Foundation will specify a dispute resolution process, utilizing an internationally accepted dispute resolution system. A rotating board of dispute referees will monitor disputes through the resolution process, \& oversee collateral release to plaintiffs. Note that this board of dispute referees is not the dispute resolution process specifically; rather it is the mechanism through which dispute resolutions can be enacted through the release of collateral on the block-chain.


\subsection{GPUCoin Token sales} % (fold)
\label{sub:hoot_token_sales}
The GPUCoin Foundation will fund the development of the GPUCoin IPCN Platform discussed in this paper through the issuance of GPUCoin tokens. These tokens will run natively on the Ethereum block-chain and will be offered to backers of the GPUCoin IPCN project via a token sale.
% The token sale will be launched on or about the November 21 2017.
A second token sale will take place once the initial prototype has been developed and tested to fund its deployment. 
\iffalse
For more information on the GPUCoin token, see \_\_\_ \fxerror{add correct section}.
\fi

\subsection{Token Allocation \& Distribution} % (fold)
\label{sub:token_allocation_and_distribution}
 The supply of GPUCoin token is limited to the number of one hundred million (100,000,000) in total (including those available for sale during the Token Sale) \& will be generated upon the launch ("Token Launch".)

 The tokens will be distributed in the following manner:
80\% (30/30/20) of the tokens will be eventually allocated amongst the community; the remaining 20\% will be allocated to the GPUCoin Foundation initiator, early backers, \& the GPUCoin protocol network development team.


\begin{table}[!htb]
\centering
\begin{tabular}{ |p{2.8cm}|p{2.5cm}|p{5cm}|}
\hline
\rowcolor{lightgray} \multicolumn{3}{|c|}{GPUCoin Token Distribution Model} \\
\hline
Channels & Percentage & Lock up Period \\
\hline
30,000,000 GPUCoin token Sale (GTS) & 30\% &
% Token Sale - Launch 21 November 2017.
The initial funding will be used to develop a working prototype, financial setup, legal fees \& promotion.
 \\
 \hline
30,000,000 Additional GPUCoin Token Sale (AGTS) & 30\% & Additional GPUCoin Token Sale. On the release of a successful prototype, a second token sale will be launched to fund the full production ready launch \& development of all relevant technology \& organization matters.
\\
\hline
20,000,000 GPUCoin tokens Retained by the GPUCoin Foundation as Treasury & 20\% & 100\% of which locked for 24 months.Strategic Planning, Project Support, Token Swap, Emergency Fund, Development \& Legal Fees - These will be subject to a 2 year lock-up. Subsequent to the lock-up, these will be used for various development \& operation costs of GPUCoin Platform over 2 further years.
\\
\hline
20,000,000 GPUCoin Advisors, Directors and Early Backers & 20\% & 70\% of which is locked for 12 months. 30\% of which is locked up for 24 months. Distributed to the directors, advisors, and early backers of the
 project.
\\
 \hline
\end{tabular}
\caption{GPUCoin Token Distribution Model}
\label{table:hoot_token_distribution_model}
\end{table}
\iffalse
\fxerror{clean up table, better formatting/fonts}
\fi

\subsection{Restriction on the use of the funds} % (fold)
\label{sub:restriction_on_the_use_of_the_funds}
To remain in line with the spirit of the project’s open and transparent philosophy, all funds shall be tracked and reported according to the GPUCoin Foundation’s guidelines. A custodian will monitor the usage of the digital tokens and share it with the community periodically.

\begin{enumerate}
 \item Financial planning and reporting
 \begin{itemize}
 \item The GPUCoin Foundation shall develop financial planning and review financial performance of the previous quarter.
 \end{itemize}

 \item Digital tokens management
 \begin{itemize}
 \item The digital tokens belonging to the GPUCoin Foundation shall be managed by authorized personnel. The security of digital tokens is ensured by multi signature technology.
 \end{itemize}

 \item Digital wallet protocol
 \begin{itemize}
 \item The GPUCoin Foundation’s digital wallet shall be protected by a multiple signature technology mechanism.
 \end{itemize}

 \item Disclosure
 \begin{itemize}
 \item On a regular basis, the GPUCoin Foundation shall disclose on the topics regarding community matters, including status of development, operations, and the usage of tokens, as well as whether the GPUCoin Foundation operates in accordance with the governance policy.
 \end{itemize}
\end{enumerate}
