\textbf{G}raphics \textbf{P}rocessing \textbf{U}nits (GPUs) can significantly accelerate the training process for many deep learning models. For example, GPUs can accelerate the training process for deep learning models designed for image classification, video analysis, \& natural language processing because the training process for those models involves the compute-intensive task of matrix multiplication and other operations that can take advantage of a GPU's massively parallel architecture. This architecture is well-suited for algorithms designed to address embarrassingly parallel workloads across more than a dozen areas of computer science \& other fields, including live streaming, VR/AR computer generated rendering, speech recognition, computer vision, robotics, information retrieval, natural language processing, geographic information extraction, \& computational drug discovery.

GPUCoin IPCN takes computations and maps them onto a wide variety of different hardware platforms, ranging from running inference on mobile device platforms such as Android \& iOS to modest-sized training \& inference systems using single machines containing one or many GPU cards to large-scale training systems running on hundreds of specialized machines with thousands of GPUs. Having a single system that can span such a broad range of platforms significantly simplifies the real-world use of GPUs, as we have found that having separate systems for large-scale GPU training \& small-scale deployment leads to significant maintenance burdens \& leaky abstractions.
% Just as TensorFlow/Keras provides a common interface for simplifying distributed AI \& machine learning, creating a thriving AI ecosystem, GPUCoin protocol provides a common interface for simplifying distributed GPU accelerated compute, thereby creating a thriving and profitable GPU cloud ecosystem backed by solid GPUCoin crypto-economics.

Training a deep learning model that involves intensive compute tasks on extremely large datasets can take days to run on a single processor. However, if you design your program to offload those tasks to one or more GPUs, you can reduce training time to hours instead of days. GPUCoin IPCN network is designed to address such embarrassingly parallel workloads and use GPUCoin GPC token as the currency of exchange \& transaction fees for these workloads using block-chain smart contracts. 

Over the past several years, advancements in Graphical Processing Unit (GPU) technology and GPU Accelerated Computing have played a significant and growing role in devices such as mobile phones, personal computers, and workstations, as well as in applications ranging from Artificial Intelligence/Machine Learning to 3D Video rendering to oil exploration to various automotive applications.  Every day, GPUs are being applied to a greater range of tasks and applications that can benefit from the chips’ ability to parallel process large blocks of data more efficiently.  GPUCoin is the instantiation of a new and innovative decentralized GPU peer-to-peer network to exploit the power unleashed by GPUs, on applications that could immediately benefit from the performance that such a network could bring to bear.  

Today’s live streaming video systems are complex to manage and difficult to scale, generally requiring proprietary broadcast software to encode captured video, high cost broadcast server software to push video fragments to expensive content delivery networks (CDNs) which cannot deliver the content in real-time.  When applying similar architectures to address the needs of Virtual Reality and Video360 applications, the high latency makes these virtually unusable.  CDNs suffer from having been conceived in the Web 1.0 wave of Web acceleration advancements, now 15-20 years old.  New GPU accelerated video encoding and decoding techniques have made significant strides in more efficiently handling the processing of video and other vector based graphics.  

