\section{Hoot Architecture}
\subsection{Broadcast Side - iOS}
Hoot protocol for realtime livestreaming video is called Real time Hoot protocol[RTHP].
Video frames are captured at a resolution of 540x960 to 720x1280 based on network connectivity. Audio stream is captured using the built in iOS device microphone at a sampling rate of 44.1 KHz. Optionally, real time filters (Black and White, Glow, Fisheye, Sepia) can be applied to captured video frames in realtime. Video and audio are encoded using the native hardware H.264 and AAC encoders, respectively. The video frames are encoded using a VBR algorithm with a maximum bitrate of 1 Mbps. Audio stream is encoded in AAC format with a bitrate of 128 Kbps. The H.264 + AAC stream is encoded into an RTHP stream and is transmitted to Hoot opensource RTHP server.

\subsection{Broadcast Side — Mac}
Video frames are captured at native screen resolution, and audio stream is captured using the built in microphone at a sampling rate of 44.1 KHz. Hoot Mac app supports capturing FaceTime, Screenshare, and a combination of FaceTime and Screenshare. Video frames and audio stream are encoded using the native H.264 and AAC encoders, respectively. The video frames are encoded with a VBR algorithm. Audio stream is encoded in AAC format with a bitrate of 128 Kbps. The H.264 + AAC stream is encoded into an RTHP stream and is transmitted to our open source RTHP server.

\subsection{Viewer Side iOS/Android }
 Hoot Open Source Native mobile media player decodes RTHP + H.264 and AAC data to make the broadcast available to viewer in real-time. The HLS (HTTP Live Streaming) stream that is made available can be played using the iOS/Android Native media players, when the Hoot RTHP player or app is not available.

\subsection{Viewer Side Mac/PC} 
The RTHP stream is played using Adobe Flash technology supported by all modern browsers. The HLS stream can be played using HTML5 player available in all modern browsers.

\subsection{Server Side}
Similar to Bitcoin blockchain technology, any node can join or leave the Hoot network at anytime. Each node serves a realtime broadcasting server.
Hoot foundation has several RTHP servers that serve to bootstrap the Network. We use commodity servers with modern processors and with 1 Gbps duplex ethernet;
No specialization of servers is needed. Our server generates two variants of streams: a RTHP stream and a HLS stream in order to make them accessible in browsers across Windows, Mac OS X, Linux and Android platforms. A server with 1 Gbps duplex ethernet can support up to a total of 1000 viewers. A stream is replicated horizontally across multiple servers (without additional latency) to stream to virtually an unlimited number of viewers. 
Streamed videos are instantly archived [H.264+AAC, mp4 container] in the cloud for later viewing. The archived videos are indexed (scrubbable). We have access to the following geographically distributed infrastructure immediately through our RTHP servers to provide the lowest latency to broadcasters and viewers around the world: Amsterdam Netherlands, Frankfurt Germany, Hong Kong, London UK, Melbourne Australia, Queretaro Mexico, Milan Italy, Montreal Canada, Toronto Canada, Paris France, Singapore, Sydney Australia, Tokyo Japan, Dallas USA, Houston USA, San Jose USA, Seattle USA, WashingtonDC USA.

